\subsection{Fallacy detection in NLP}
\label{sec:bg-fallacy}

The Reddit informal-fallacy dataset that the Touch\'{e} 2026 lab redistributes was introduced by Sahai et al.~\cite{sahai2021invisiblewall}, who labelled a long-tail eight-way taxonomy over comments mined from r/changemyview and adjacent subreddits and reported the first transformer baselines on the resulting corpus. Adjacent benchmarks treat closely related phenomena with similar fine-grained label structures. The Argument Reasoning Comprehension task introduced multi-class warrant identification on user-written argument pairs and surfaced how brittle large language models can be on argumentation tasks that require implicit-premise reasoning~\cite{habernal2018arc}. Da San Martino et al.~\cite{dasanmartino2019propaganda} catalogued eighteen propaganda techniques in news articles. Several of those techniques (\emph{appeal to authority}, \emph{appeal to fear}, \emph{black-and-white fallacy}) overlap directly with the ST2 inventory and indicate that the propaganda-detection literature is a useful cross-domain reference even though the source genre differs. Goffredo et al.~\cite{goffredo2022political} classified fallacies in political-debate transcripts and are the most direct lineage of the ST2 classifier we extend. Their reported difficulty in distinguishing \emph{hasty generalisation} from \emph{appeal to population} mirrors what we observed in our own confusion structure.

Two more recent papers anchor the picture. Alhindi et al.~\cite{alhindi2022multitask} reported the strongest prior multitask instruction-prompted results on the Sahai et al.\ data, demonstrating that multitask supervision over related fallacy datasets transfers usefully to the eight-way Reddit task. MAFALDA~\cite{helwe2024mafalda} is the most-cited 2024 unified fallacy benchmark, we do not retrain on MAFALDA, but our ST2 label inventory is recognisable in its taxonomy and the MAFALDA error-analysis findings on rare-class behaviour echo what we report for the ST3 \textsf{pe} class in \S\ref{sec:disc-pe}. Pan et al.~\cite{pan2024zeroshotfallacy} provide the published precedent for evaluating LLMs as zero-shot fallacy classifiers. They show that zero-shot LLM performance is real but uneven across fallacy types, which motivates the LLM track we describe in \S\ref{sec:llm-detour} as worth running rather than dismissing.

\subsection{Argumentation schemes}
\label{sec:bg-schemes}

The four ST3 labels are not an ad-hoc taxonomy. They sit inside the Walton--Reed--Macagno scheme catalogue~\cite{walton2008schemes}, which has been the canonical taxonomic backbone for argumentation theory for nearly two decades and which organises argumentation patterns by the conjunction of a goal (what the argument is for) and a basis (what the argument rests on). The four-cell split we use on ST3 (practical / epistemic $\times$ internal / external) is operationalised by the lab task description~\cite{kiesel:2026c}. Its conceptual antecedents are the argumentation-profile framing of Macagno~\cite{macagno2022argumentation} and the broader scheme catalogue of Walton, Reed, and Macagno~\cite{walton2008schemes}. The crossing reflects whether the speaker is arguing about what to do or what to believe, and whether their warrant comes from the speaker's own resources or from an external source. Jo et al.~\cite{jo2021schemes} is, to our knowledge, the cleanest NLP-on-Walton-schemes prior work and the only one whose label set overlaps non-trivially with ST3. The shelf of comparable NLP work is thin, which is part of what makes the task interesting and also part of what means a system designer cannot transfer published model recipes directly.

The Touch\'{e} lab itself has progressively shifted over recent editions from argument retrieval~\cite{bondarenko2022touche,bondarenko2023touche} to full argumentation systems~\cite{kiesel2024touche,kiesel2025touche}, with the 2026 edition the first to feature fallacy detection as a dedicated task. The encoder-vs-LLM trade-off for small-corpus fallacy classification is not, to our reading, settled by the published literature: encoder fine-tuning, LoRA-adapted mid-size LLMs, and zero/few-shot prompted frontier models have each been reported as competitive on neighbouring tasks, with no clean recipe-matched comparison at the corpus scale of the present shared task. That open question is the gap our contribution C3 addresses, and it motivates the systematic backbone comparison reported in \S\ref{sec:results}.
