\subsection{Pipeline overview}
\label{sec:pipeline}

The pipeline has three input streams feeding one fine-tuned encoder: real examples, synthetic contrastive pairs, and a gated pseudo-labelled top-up --- a small batch of extra training items that the encoder labels itself from the published unlabelled data, kept only for the examples it is most confident about and only after a verification check has passed. \S\ref{sec:backbone} fixes the backbone (supporting C1), \S\ref{sec:synth}--\S\ref{sec:pseudo} build the two augmented streams (supporting C2), and \S\ref{sec:llm-detour} reports the LLM alternative we evaluated against this pipeline (supporting C3). Our main focus this year was on building a uniform fine-tuning pipeline that we could apply, with minimal cell-specific variation, across every (subtask, track) combination the lab requires. The Touch\'{e} 2026 lab~\cite{kiesel:2026c} (task description and labels at \url{https://touche.webis.de/clef26/touche26-web/fallacy-detection.html}) defines three subtasks over the Reddit informal-fallacy data of Sahai et al.~\cite{sahai2021invisiblewall}, with evaluation hosted on TIRA~\cite{froebe:2023}. Subtask ST1 is a binary decision on whether a given comment, presented together with its parent comment and the title of the originating thread, commits any informal fallacy. Subtask ST2 conditions on a positive ST1 decision and asks for the specific fallacy type from an eight-way inventory (using the official label strings from the task schema): \textsf{authority}, \textsf{black-white}, \textsf{hasty-generalization}, \textsf{natural}, \textsf{population}, \textsf{slippery-slope}, \textsf{tradition}, \textsf{worse-problems}. Subtask ST3 conditions on a negative ST1 decision and asks for the argument scheme of the comment from a four-way inventory~\cite{walton2008schemes,macagno2022argumentation}: \textsf{practical-internal}, \textsf{practical-external}, \textsf{epistemic-internal}, \textsf{epistemic-external}, which we abbreviate \textsf{pi}, \textsf{pe}, \textsf{ei}, \textsf{ee} respectively in the rest of the paper. Evaluation is by macro-averaged F1 in all three subtasks, which puts roughly equal weight on each label and turns rare-class behaviour into a binding constraint on the headline number, a point we return to in \S\ref{sec:disc-pe}. Each subtask is evaluated in two tracks. The \emph{base} track exposes only original Reddit fields (in our setup, \texttt{text\_raw}, \texttt{text\_raw\_parent}, \texttt{text\_raw\_title}, \texttt{text\_base}, \texttt{argument\_base}). The \emph{enhanced} track additionally exposes two organiser-supplied paraphrases, \texttt{text\_enhanced} and \texttt{argument\_enhanced}, that were rewritten with knowledge of the gold labels in order to make the argumentative structure of the comment more explicit, and is scored as a separate track from the base submissions. The rewrite is a designed feature; we defer the characterisation of how much label-bearing signal it carries to \S\ref{sec:disc-leakage}, where the analysis sits in one place. The lab permits up to three runs per (subtask, track), for a maximum of nine submissions. We used six, populating one slot per subtask per track. Appendix~\ref{app:citgraph} traces which prior work motivated each component of the pipeline described below.

\begin{figure}[h]
\centering
\begin{tikzpicture}[
  every node/.style={font=\scriptsize, align=center},
  box/.style={rectangle, draw=black!70, line width=0.4pt,
              rounded corners=2pt, inner sep=2pt,
              minimum width=20mm, minimum height=8mm},
  inp/.style={box, fill=black!4},
  proc/.style={box, fill=black!8},
  arr/.style={-{Latex[length=1.6mm]}, line width=0.4pt},
  lbl/.style={midway, sloped, above, font=\tiny, inner sep=1pt}
]
% Left column: three input streams stacked vertically
\node[inp] (real)    at (0,  1.8) {Real\\examples};
\node[inp] (synth)   at (0,  0)   {Synthetic\\contrastive pairs};
\node[inp] (pool)    at (0, -1.8) {Unlabelled pool\\(enhanced only)};
% Bottom-row chain: confidence-thresholded audit + pseudo-labelled
\node[proc] (gate)   at (3.0, -1.8) {Audit gate\\\texttt{exp\_0081}};
\node[inp]  (pseudo) at (6.0, -1.8) {Pseudo-\\labelled};
% Central mixer
\node[proc] (mix)    at (6.0,  0)   {Mini-batch\\mix};
% Right pair: encoder, head
\node[proc] (enc)    at (9.0,  0)   {RoBERTa-large\\encoder};
\node[proc] (head)   at (12.0, 0)   {Per-task head\\(argmax)};
% Arrows into mixer, with per-stream sw labels
\draw[arr] (real)   -- node[lbl] {\texttt{sw=1.0}} (mix);
\draw[arr] (synth)  -- node[midway, above, font=\tiny, inner sep=1pt] {\texttt{sw=0.5}} (mix);
\draw[arr] (pool)   -- (gate);
\draw[arr] (gate)   -- (pseudo);
\draw[arr] (pseudo) -- node[lbl] {per-cell \texttt{sw}} (mix);
% Right-side flow
\draw[arr] (mix)  -- (enc);
\draw[arr] (enc)  -- (head);
\end{tikzpicture}
\caption{Training and inference pipeline for the submitted RoBERTa-large systems.
Real, synthetic, and pseudo-labelled examples are mixed at per-stream loss weights
(real at 1.0; the synthetic and pseudo-labelled streams down-weighted per cell,
see Appendix~\ref{app:hyper}) into a single fine-tuning loop. The audit gate sits between
pseudo-label generation and pseudo-label training (\S\ref{sec:pseudo}). At inference time the trained
classifier head is decoded with per-class thresholds for ST3 and default argmax
for ST1/ST2.}
\label{fig:pipeline}
\end{figure}

The same pipeline produces all six submitted runs, with per-cell hyperparameters summarised in Appendix~\ref{app:hyper}. Real examples are concatenated from the published Reddit fields, augmented with a small batch of LLM-generated synthetic contrastive pairs (\S\ref{sec:synth}), and for ST2 and ST3 enhanced extended with pseudo-labelled unlabelled examples (\S\ref{sec:pseudo}) once the dev-overlap audit has passed. The three input streams are interleaved in each training mini-batch under the per-stream loss weights given in the caption. The mixed corpus is fed into a RoBERTa-large encoder~\cite{liu2019roberta} with a task-specific classification head. Loss is class-weighted cross-entropy for ST2 and ST3 (with class weights set to inverse-frequency on the training partition) and unweighted cross-entropy for ST1. We use the HuggingFace \texttt{transformers} library throughout~\cite{wolf2020transformers}, with the AdamW optimiser, a linear warmup over the first 10\% of steps, and a peak learning rate of 1e-5. Inference uses default argmax over class logits for all three subtasks, including the submitted ST3 runs. We additionally explored a per-class threshold sweep on the ST3 development partition (\S\ref{sec:thresholds}) as a diagnostic, but did not apply it to the uploaded predictions. The same training loop is used for all six (subtask, track) cells. Only the input fields, the loss weights, the truncation length, and the presence or absence of pseudo-labelled examples vary across cells. Inputs are concatenated using the standard RoBERTa special tokens \texttt{<s>...</s></s>...</s>}, with tokeniser truncation set to \texttt{max\_len=384} for ST3, \texttt{max\_len=256} for ST1 enhanced and both ST2 cells, and \texttt{max\_len=512} for the submitted ST1-base run (\texttt{exp\_0161}), which concatenates \texttt{text\_raw} with \texttt{text\_base}. The choice between these windows was driven by a token-length diagnostic showing that ST3 inputs benefited measurably from the longer window once \texttt{argument\_enhanced} was concatenated, while the shorter ST1-enhanced and ST2 inputs fit comfortably inside 256 with only a small tail of truncations. % from exp_0069 exp_0073 exp_0033 exp_0035 exp_0032 exp_0061

\subsection{Backbone selection}
\label{sec:backbone}

We compared RoBERTa-base, RoBERTa-large, DeBERTa-v3-base, DeBERTa-v3-large, and ModernBERT-large under matched data and training budgets. RoBERTa-large beat RoBERTa-base by 0.027 on ST1 base, 0.007 on ST1 enhanced, and 0.055 on ST2 base under matched recipes. % from exp_0013 exp_0004 exp_0022 exp_0016 exp_0014 exp_0005
The one cell where RoBERTa-base was marginally ahead, ST2 enhanced (0.925 vs.\ 0.923), sits inside seed-variance for these models and we treat it as a tie rather than evidence against the larger backbone. % from exp_0017 exp_0023
We therefore standardised on RoBERTa-large for the six submitted runs.

DeBERTa-v3-large did not survive the fine-tuning recipes we tried. Plain dev runs collapsed to near-chance F1 across all three subtasks (ST1 base 0.351, ST2 base 0.030, ST3 base 0.205 across two attempts). % from exp_0007 exp_0008 exp_0009 exp_0040
Mixed-precision training NaN-exploded across four subtask$\times$sw combinations. Switching to bf16 with a smaller learning rate stopped the NaNs but produced near-zero F1. % from exp_0041 exp_0042 exp_0043 exp_0044 exp_0049 exp_0050 exp_0051
After four NaN-explosion incidents and seven collapse-or-fail runs, we removed DeBERTa-v3-large from the backbone shortlist.

ModernBERT-large~\cite{warner2024modernbert} ran cleanly but did not beat RoBERTa-large on ST3 enhanced, reaching 0.719 against RoBERTa-large's 0.735. % from exp_0086 exp_0073
A 0.016 F1 gap on a 4-way task is real but not enough to override the simpler, well-understood RoBERTa pipeline for a notebook-paper submission. For a corpus of roughly 473 ST3 examples, RoBERTa-large is the rational choice. We revisit the LLM alternatives in \S\ref{sec:llm-detour} and \S\ref{sec:disc-encoder}.

\subsection{Synthetic data augmentation}
\label{sec:synth}

We generated synthetic contrastive pairs using a frontier LLM via API. The lab data additionally ships a \texttt{resembles\_fallacy} field that pairs each non-fallacious comment with a structurally similar fallacy class, exactly the near-miss contrast our synthetic pairs are designed to manufacture; we did not consume that field as an explicit training signal, and treating it as a built-in contrastive supervision channel for ST1 is a natural follow-up we leave for a future submission~\cite{kiesel:2026c}. For each target label, we prompted the model with three real in-domain examples and asked it to produce a paired contrast, a minimally edited rewrite that flips the label while preserving topic, register, and Reddit-conversational style. Generations were filtered by a length sanity check and a string-overlap heuristic against the source pair to discourage trivial copies. Three batches were produced: an initial \texttt{synth\_v002} (130 pairs for ST1/ST2 and 110 pairs for ST3); a rare-class top-up \texttt{synth\_v003} for ST3 (100 epistemic-external + 50 practical-external pairs); and a separate \textsf{pe}-targeted batch (100 practical-external + practical-anchor pairs).\footnote{The exact prompt template and the generated pairs are released alongside this notebook in the TIRA submission package.} % from exp_0025 exp_0030 exp_0056 exp_0103

Synth at \texttt{sw=0.5} added 0.014--0.019 F1 across the four ST1 and ST2 cells (Table~\ref{tab:ablation}). % from exp_0013 exp_0033 exp_0022 exp_0035 exp_0014 exp_0032 exp_0023 exp_0036
On ST3 enhanced, however, synth alone did not move the needle: the real-only baseline and the +synth configuration tied at 0.694, and the eventual gain on this cell only appeared once pseudo-labelling was added (\S\ref{sec:pseudo}). % from exp_0024 exp_0067

The largest single gain came on ST3 base, where the \texttt{synth\_v002} recipe at \texttt{max\_len=384} lifted F1 from 0.436 to 0.523, an improvement of +0.087. % from exp_0058 exp_0069
Synth is not a free lunch: adding the \texttt{synth\_v003} rare-class top-up on top of \texttt{synth\_v002} dropped ST3-base F1 by 0.045 relative to \texttt{synth\_v002} alone, and a focal-loss recipe~\cite{lin2017focal} lost 0.018 over the same baseline. % from exp_0068 exp_0069 exp_0053
We read this as confirmation of the general caveat documented by Li et al.~\cite{li2023synthdata}: synthetic data improves the average and harms the worst-case, and which side you land on depends on the recipe.

\subsection{Pseudo-labelling}
\label{sec:pseudo}

For ST2 and ST3 enhanced we additionally added pseudo-labelled examples drawn from the published unlabelled pool. Predictions from the best dev-F1 checkpoint at the matching subtask $\times$ track were filtered by confidence at a nominal threshold $\tau=0.9$ (relaxed for under-populated classes so that rare schemes were not dropped entirely) and added to the training mix as an additional down-weighted stream; the per-cell loss weights are listed in Appendix~\ref{app:hyper}.\footnote{The pseudo-label confidence threshold $\tau$ and the source checkpoint are released in the TIRA reproducibility package alongside the prompt template.} Following the modern transformer-era treatment by Mukherjee and Awadallah~\cite{mukherjee2020ust} and the original pseudo-label idea of Lee~\cite{lee2013pseudolabel}, we treated this step with caution: pseudo examples are drawn from the unlabelled pool and could in principle be near-duplicates of dev instances, inflating the dev score, so we ran a dedicated dev-overlap audit (\texttt{exp\_0081}) before letting them into training. It checked id-level, exact-text, and token-Jaccard overlap between the pseudo-labelled entries and the dev split, and found no id or exact-text overlap and no token-Jaccard pair above 0.5 (maximum 0.30); we proceeded. % from exp_0081
The recipe paid off most clearly on ST2 enhanced, where adding pseudo lifted F1 from 0.937 to 0.970, a gain of +0.033 over the synth-only baseline. % from exp_0036 exp_0072
On ST3 enhanced the same recipe at \texttt{max\_len=384} lifted F1 from 0.694 to 0.735, a gain of +0.041 over the closest matching synth-only baseline. % from exp_0073
The pseudo recipe at \texttt{max\_len=256} underperformed its synth-only counterpart on ST1 enhanced (0.906 against 0.914, a loss of 0.008), % from exp_0071
which is one of the reasons we did not adopt pseudo for ST1 enhanced in the final submission.

A first diagnostic on ST3 used an NLI-style basis probe whose per-class breakdown surfaced a clear weakness: \textsf{pe} F1 was 0.25, well below the other three classes. % from exp_0082
That number was what motivated the \textsf{pe}-targeted synth batch above. After training the final ST3-enhanced classifier, we ran a per-class threshold sweep on the dev partition as a diagnostic; the best configuration $\{\text{ee}=0.1, \text{ei}=0.1, \text{pe}=0.05, \text{pi}=0.4\}$ added +0.026 F1 over default argmax on that partition. The submitted ST3 predictions use argmax; we did not apply these thresholds to the uploaded runs. % from exp_0145
A subsequent attempt to learn a basis-axis meta-learner from LLM signals gave no improvement over the encoder-only weighted average and was not used in the submission. % from exp_0146
\label{sec:thresholds}
The exact synthetic-pair generation prompts can be seen in Appendix~\ref{app:prompts}.

\subsection{The LLM alternative}
\label{sec:llm-detour}

Encoders did not look like the obvious choice at the start of the project. Following the published precedent of Pan et al.~\cite{pan2024zeroshotfallacy}, whose zero-shot LLM results are reported on different fallacy corpora and are therefore not directly numerically comparable, we ran a zero-shot Qwen2.5-3B baseline on ST3 enhanced, which reached F1 0.47, well below the RoBERTa baselines of \S\ref{sec:backbone}. % from exp_0091
A kNN few-shot variant retrieving over a \texttt{bge-large-en-v1.5} sentence embedding index (1876$\times$1024) recovered some ground at 0.53, but still trailed RoBERTa-large by a wide margin. % from exp_0138 exp_0143

We then trained CoT-LoRA recipes~\cite{hu2022lora,dettmers2023qlora,wei2022cot} on Qwen2.5-7B and Qwen2.5-32B. The 7B 5-fold CV on ST3 enhanced reached 0.85 $\pm$ 0.11; the 32B single-run reached 0.84. % from exp_0180 exp_0207
We also evaluated Qwen3-4B-Thinking~\cite{qwen3}: its 5-fold CV reached 0.96 on ST2 enhanced, which is competitive with the submitted encoder, but on ST3 base the same model reached only 0.45, below the 0.52 we already had with RoBERTa-large under the \texttt{synth\_v002} recipe. % from exp_0217 exp_0218

Despite the apparent competitiveness of the larger configurations on individual cells, the CoT-LoRA configurations we evaluated did not show a validated benefit over the encoder within our compute envelope. Our final submission (\texttt{exp\_0220}) populates all six slots with RoBERTa-large systems. % from exp_0220
