We report both our held-out development results, on which all system-selection decisions were made, and the official Touch\'{e} 2026 test-set leaderboard results (\S\ref{sec:test}, Table~\ref{tab:test}). Development numbers are macro-averaged F1 on the held-out partition or, where flagged, the mean of a 5-fold cross-validation on that partition; all six submitted runs use recipes fixed before the test labels were released. Unless a number is explicitly labelled a test result, it is a development number.

\subsection{Validation Results}
\label{sec:headline}

Following the official Touch\'{e} 2026 release, we work from the published labelled pool for each subtask: 938 examples for ST1, the 465-example fallacious subset for ST2, and 473 non-fallacious examples for ST3. % from exp_0124
From each pool we hold out a stratified 15\% development split (ST1 $n=139$, ST2 $n=67$, ST3 $n=69$) on which the single-run headline numbers in Table~\ref{tab:headline} are computed, training on the remainder; the 5-fold cross-validation runs instead cross-validate over the full ST3 pool. This distinction is load-bearing for ST3: the single dev split holds exactly one \textsf{pe} example (Appendix~\ref{app:perclass}), so its macro-F1 is dragged down by that one always-hard cell, whereas 5-fold CV distributes \textsf{pe} across folds. This is the main reason the ST3-enhanced CV mean ($0.875$, \S\ref{sec:final-submission}) sits well above the single-split dev and five-seed estimates ($0.735$ and $0.720 \pm 0.015$). % from exp_0124 exp_0153
Class distributions follow the underlying Sahai et al.\ data and are long-tailed; the ST3 \textsf{pe} class in particular is small enough to be the binding constraint on macro-F1, which we revisit in \S\ref{sec:disc-pe}.

Table~\ref{tab:headline} reports precision, recall, and F1-macro on our held-out development partition for the six submitted runs. Each row carries the precision, recall, and F1-macro for one (subtask, track) cell, with macro-averaging over the 8- and 4-class label sets for ST2 and ST3 respectively; the two enhanced-track values should be read in light of the rewriter-signal discussion in \S\ref{sec:disc-leakage}. % from R2-m1
Across the six cells the easier binary task and the hardest scheme task differ by roughly 0.2 F1 on each track, and the base-to-enhanced gap varies markedly across subtasks.

\begin{table}[h]
\centering
\small
\caption{Headline dev results for the six submitted runs. P, R, F1 are macro-averaged
for ST2 and ST3. The two enhanced-track values should be read with the
caveat of \S\ref{sec:disc-leakage} on the enhanced-track signal.}
\label{tab:headline}
\begin{tabular}{llcccl}
\toprule
Subtask & Track & Precision & Recall & F1 & exp\_id \\
\midrule
ST1 & base     & 0.769 & 0.762 & 0.761 & exp\_0161 \\ % from exp_0161
ST1 & enhanced & 0.917 & 0.914 & 0.914 & exp\_0035 \\ % from exp_0035
ST2 & base     & 0.746 & 0.728 & 0.730 & exp\_0032 \\ % from exp_0032
ST2 & enhanced & 0.970 & 0.972 & 0.970 & exp\_0072 \\ % from exp_0072
ST3 & base     & ---   & ---   & 0.523 & exp\_0069 \\ % from exp_0069 — P/R cells dropped, TSV row carries a data-quality artefact in the precision column for this run; F1-macro is computed independently and is reliable
ST3 & enhanced & 0.732 & 0.740 & 0.735 & exp\_0073 \\ % from exp_0073
\bottomrule
\end{tabular}
\end{table}

On ST3 we additionally ran 5-fold cross-validation under our submitted recipe (fold seeds 42--46), which gave mean F1 0.875 with the same configuration. % from exp_0073 exp_0153
The Qwen2.5-7B CoT-LoRA alternative for ST3 enhanced gave 0.851 $\pm$ 0.114 over the same fold split. The standard deviation overlaps the RoBERTa CV mean, which is the decision-relevant fact behind the final-submission rationale we discuss below. % from exp_0180
Of the six numbers, the ST2-enhanced cell is simultaneously the numerically strongest result in this paper and the one in which we have the least interpretive confidence. We address this directly in \S\ref{sec:disc-leakage}.

\subsection{Official test-set results}
\label{sec:test}

Table~\ref{tab:test} reports the official Touch\'{e} 2026 test-set leaderboard scores for our six submitted runs, together with our placement among participating teams on each (subtask, track) cell. These are the final evaluation numbers; the recipes were fixed on the development evidence above before the test labels were released.

\begin{table}[h]
\centering
\small
\caption{Official Touch\'{e} 2026 test-set results for the six submitted runs
(macro-averaged precision, recall, F1). \emph{Rank} is our placement among
participating teams on that (subtask, track) cell. Bold marks the two cells we
ranked first on.}
\label{tab:test}
\begin{tabular}{llcccc}
\toprule
Subtask & Track & Precision & Recall & F1 & Rank \\
\midrule
ST1 & base     & 0.770 & 0.754 & 0.751          & 2 \\
ST1 & enhanced & 0.946 & 0.945 & 0.944          & 2 \\
ST2 & base     & 0.876 & 0.860 & \textbf{0.859} & \textbf{1} \\
ST2 & enhanced & 0.958 & 0.954 & 0.954          & 6 \\
ST3 & base     & 0.710 & 0.724 & \textbf{0.716} & \textbf{1} \\
ST3 & enhanced & 0.716 & 0.933 & 0.748          & 5 \\
\bottomrule
\end{tabular}
\end{table}

Our uniform encoder pipeline ranked \emph{first} on both base-track classification cells --- ST2 base (0.859) and ST3 base (0.716) --- and \emph{second} on both binary-detection tracks (ST1 base 0.751, ST1 enhanced 0.944). On the two enhanced-track classification cells it placed lower (ST2 enhanced 0.954, sixth; ST3 enhanced 0.748, fifth), where the leading systems were a cascaded pipeline (\textsf{uzh-tt}, 0.991 on ST2 enhanced) and a multitask DeBERTa (\textsf{sevitha}, 0.976 on ST3 enhanced).

Two patterns are worth drawing out. First, the base-track test numbers came in well above their development estimates: ST3 base rose from a dev 0.523 to a test 0.716, and ST2 base from 0.730 to 0.859, while the enhanced-track cells tracked their dev numbers closely (ST3 enhanced 0.735 dev vs.\ 0.748 test; ST2 enhanced 0.970 vs.\ 0.954). This is consistent with the small held-out dev splits (\S\ref{sec:headline}) underestimating base-track performance rather than with any test-time surprise. Second, the single-encoder recipe was most competitive exactly where the enhanced rewrite is unavailable --- the base tracks --- while on the enhanced tracks systems built to exploit the rewritten fields, by cascading or multitasking over them, pulled ahead; this is the same label-bearing signal we characterise in \S\ref{sec:disc-leakage}, seen from the leaderboard side.

\subsection{Binary Fallacy Detection (ST1)}
\label{sec:results-st1}

The binary task was the easiest of the three. The submitted ST1-base run (\texttt{exp\_0161}) concatenates \texttt{text\_raw} with \texttt{text\_base} at \texttt{max\_len=512} and reached F1 0.761 on the dev partition. The synthetic-data contribution is isolated separately in Table~\ref{tab:ablation} at \texttt{max\_len=256}, where +\texttt{synth\_v002} at \texttt{sw=0.5} lifts F1 from a real-only baseline of 0.716 to 0.734 (\texttt{exp\_0033}). % from exp_0161 exp_0013 exp_0033
On the enhanced track, the same synth recipe reached 0.914 against a real-only enhanced baseline of 0.899, with the +synth lift contributing +0.015 over that baseline. % from exp_0022 exp_0035
A pseudo-labelling extension at \texttt{max\_len=256} and \texttt{sw=0.5} underperformed its synth-only counterpart by 0.008 (Table~\ref{tab:ablation}, row $-$0.008), which is the reason ST1 enhanced ships under synth only rather than synth + pseudo. % from exp_0071
The 0.15 base-to-enhanced gap on ST1 previews the enhanced-track signal discussion of \S\ref{sec:disc-leakage}.

\subsection{Eight-Way Fallacy Classification (ST2)}
\label{sec:results-st2}

ST2 fallacy classification is comparably easy on the enhanced track (0.97) and substantially harder on the base track (0.73), the largest base-to-enhanced gap in Table~\ref{tab:headline}. On the base track the submitted +synth configuration reached 0.730 over a real-only baseline of 0.711 (+0.019). % from exp_0014 exp_0032
On the enhanced track, the +synth configuration alone reached 0.937 against a real-only enhanced baseline of 0.923 (+0.014), and the +synth+pseudo recipe at \texttt{max\_len=384} and \texttt{sw=0.3} added another +0.033 on top of that to reach 0.970. % from exp_0023 exp_0036 exp_0072
Per-class precision and recall for ST2-enhanced are reported in Appendix~\ref{app:perclass}; on the $n=67$ dev split the eight classes range from 0.889 to 1.000 F1, with five of the eight at 1.000 --- a high, tight distribution consistent with the rewriter carrying strong label-bearing signal as discussed in \S\ref{sec:disc-leakage}.

\subsection{Four-Way Argument Schemes (ST3)}
\label{sec:results-st3}

ST3 argument-scheme classification was the hardest on both tracks, at 0.523 base and 0.735 enhanced; the four-way scheme task absorbed the bulk of our experimental effort and is the cell where the per-class behaviour discussed in \S\ref{sec:disc-pe} matters most. On the base track, the +\texttt{synth\_v002} recipe at \texttt{max\_len=384} lifted F1 from a real-only baseline of 0.436 to 0.523 (+0.087, the largest single ablation gain in the paper). % from exp_0058 exp_0069
On the enhanced track, the +synth+pseudo recipe at the same window (with the augmented streams left at full weight, \texttt{sw=1.0}) reached 0.735 against a real-only enhanced baseline of 0.694 (+0.041); +synth alone tied the real-only baseline on this cell, so the gain only appeared once pseudo-labelling was added. % from exp_0024 exp_0067 exp_0073
Two ST3-base recipes lost ground in the ablation: the \texttt{synth\_v002 + v003} stack at \texttt{max\_len=384} dropped to 0.478 ($-$0.045 against \texttt{synth\_v002} alone), and the focal-loss variant reached 0.505 ($-$0.018 against the same baseline). % from exp_0068 exp_0053

\begin{table}[h]
\centering
\small
\caption{Per-subtask augmentation ablation, F1-macro on dev. $\Delta$ is the change
relative to the immediately preceding row within the same (subtask, track) block.
The shorthand \texttt{@N} denotes \texttt{max\_len=N} (tokeniser truncation length).
Negative deltas are not hidden.\textsuperscript{a}Single-seed unless noted; see \S\ref{sec:limitations} for the seed-variance caveat.}
\label{tab:ablation}
\begin{tabular}{llllcr}
\toprule
Subtask & Track & Recipe & exp\_id & F1 & $\Delta$ \\
\midrule
ST1 & base     & real only                          & exp\_0013 & 0.716 & ---     \\ % from exp_0013
ST1 & base     & + synth (sw=0.5)                   & exp\_0033 & 0.734 & +0.018 \\ % from exp_0033
\addlinespace
ST1 & enhanced & real only                          & exp\_0022 & 0.899 & ---     \\ % from exp_0022
ST1 & enhanced & + synth (sw=0.5)                   & exp\_0035 & 0.914 & +0.015 \\ % from exp_0035
ST1 & enhanced & + synth + pseudo @256 (sw=0.5)     & exp\_0071 & 0.906 & $-$0.008 \\ % from exp_0071
\midrule
ST2 & base     & real only                          & exp\_0014 & 0.711 & ---     \\ % from exp_0014
ST2 & base     & + synth (sw=0.5)                   & exp\_0032 & 0.730 & +0.019 \\ % from exp_0032
\addlinespace
ST2 & enhanced & real only                          & exp\_0023 & 0.923 & ---     \\ % from exp_0023
ST2 & enhanced & + synth (sw=0.5)                   & exp\_0036 & 0.937 & +0.014 \\ % from exp_0036
ST2 & enhanced & + synth + pseudo @384 (sw=0.3)     & exp\_0072 & 0.970 & +0.033 \\ % from exp_0072
\midrule
ST3 & base     & real only                          & exp\_0058 & 0.436 & ---     \\ % from exp_0058
ST3 & base     & + synth\_v002 @384                 & exp\_0069 & 0.523 & +0.087 \\ % from exp_0069
ST3 & base     & + synth\_v002 + v003 @384          & exp\_0068 & 0.478 & $-$0.045 \\ % from exp_0068
ST3 & base     & + synth\_v002 + focal loss         & exp\_0053 & 0.505 & $-$0.018 \\ % from exp_0053
\addlinespace
ST3 & enhanced & real only                          & exp\_0024 & 0.694 & ---     \\ % from exp_0024
ST3 & enhanced & + synth @384                       & exp\_0067 & 0.694 & 0.000  \\ % from exp_0067
ST3 & enhanced & + synth + pseudo @384 (sw=1.0)     & exp\_0073 & 0.735 & +0.041 \\ % from exp_0073
\bottomrule
\end{tabular}
\end{table}

Augmentation strategies are recipe-sensitive: synth alone gives consistent small gains on ST1/ST2 and the largest single gain on ST3 base, while pseudo-labelling unlocks the enhanced track for ST2 and ST3 but costs on ST1 enhanced under the pseudo recipe. The \texttt{synth\_v003} top-up on ST3 base and the focal-loss recipe on ST3 base illustrate the same lesson at smaller scale. We keep the losses in the same table rather than relegating them to a footnote.

Table~\ref{tab:backbone} reports the most informative subset of the backbone runs we evaluated on ST3, with one ST3-base and one ST2-enhanced LLM row included for context. Each row is a single dev-partition F1 unless flagged otherwise. The cross-validated rows are 5-fold means. The cross-row variability is wide enough that the comparison should be read alongside the cross-validation evidence in the prose below, not as a clean ranking.

\begin{table}[h]
\centering
\small
\caption{Backbone comparison on ST3 enhanced (and one ST3 base + one ST2 enhanced
LLM row for context). Single-run dev F1 unless otherwise noted. The submitted
row is marked $\dagger$. \textsc{collapsed} = recipe failed to train.}
\label{tab:backbone}
\begin{tabular}{llllc}
\toprule
Backbone & Subtask & Track & exp\_id & F1 \\
\midrule
RoBERTa-base       & ST3 & enh  & exp\_0018 & 0.675 \\ % from exp_0018
RoBERTa-large$^{\dagger}$  & ST3 & enh  & exp\_0073 & 0.735 \\ % from exp_0073
DeBERTa-v3-base    & ST3 & base & exp\_0003 & 0.277 \\ % from exp_0003
DeBERTa-v3-large   & ST3 & base & exp\_0009 & 0.205 \\ % from exp_0009 (collapsed)
ModernBERT-large   & ST3 & enh  & exp\_0086 & 0.719 \\ % from exp_0086
Qwen2.5-3B zero-shot      & ST3 & enh & exp\_0091 & 0.467 \\ % from exp_0091
Qwen2.5-3B kNN few-shot   & ST3 & enh & exp\_0143 & 0.529 \\ % from exp_0143
Qwen2.5-7B CoT-LoRA (5-fold CV)  & ST3 & enh  & exp\_0180 & 0.851 $\pm$ 0.114 \\ % from exp_0180
Qwen2.5-32B CoT-LoRA (single)    & ST3 & enh  & exp\_0207 & 0.841 \\ % from exp_0207
Qwen3-4B-Thinking (5-fold CV)    & ST2 & enh  & exp\_0217 & 0.963 \\ % from exp_0217
Qwen3-4B-Thinking (5-fold CV)    & ST3 & base & exp\_0218 & 0.448 \\ % from exp_0218
\bottomrule
\end{tabular}
\end{table}

Reading the table top to bottom, RoBERTa-large at the second row is the submitted system (the dagger marks it). RoBERTa-base sits 0.06 F1 below it, which is the empirical justification for paying the larger backbone's compute cost. Of all the routes we tried, the DeBERTa-v3 column was the most problematic: DeBERTa-v3-base reached only 0.277 on ST3 base, and DeBERTa-v3-large failed to train at all, collapsing to 0.205 with a NaN-explosion history we detail in \S\ref{sec:backbone}. ModernBERT-large at 0.719 is the next-best encoder route but loses 0.016 F1 on the cell we evaluated. The Qwen rows tell their own story: the 3B zero-shot configuration trails RoBERTa-large by 0.27 F1; kNN few-shot recovers some ground but still trails by 0.21; the fine-tuned 7B and 32B CoT-LoRA configurations close most of the gap on a single run, but the 7B 5-fold standard deviation of $\pm$0.114 is wide enough that the comparison is statistically inconclusive at our sample size. The Qwen3-4B-Thinking comparator is the mixed result that complicates a clean encoder-beats-LLM headline: competitive on ST2 enhanced under cross-validation, but below the RoBERTa baseline on ST3 base.

The per-class F1 distribution for the submitted ST3-enhanced system is reported in Appendix~\ref{app:perclass} (\textsf{ee} 1.000, \textsf{ei} 0.979, \textsf{pi} 0.963, \textsf{pe} 0.000), computed under argmax on the $n=69$ dev split, and discussed in \S\ref{sec:disc-pe}. The \textsf{pe} cell rests on a single dev example and is therefore uninformative; we rely on the 5-fold cross-validation (\S\ref{sec:disc-pe}) for any \textsf{pe} characterisation. The submitted run's dev logits were not checkpointed, so its exact confusion matrix cannot be recovered. We have since added dev-logit checkpointing to the training script and re-ran the \texttt{exp\_0073} recipe under five seeds on the same fixed dev split, both to characterise run-to-run variance and to recover a representative confusion matrix (Table~\ref{tab:st3cm}). Across the five re-runs dev macro-F1 is $0.720 \pm 0.015$ (range $0.700$--$0.741$, all fifteen epochs completed), which places the submitted $0.735$ near the top of the observed range and is consistent with the single-run caveat of \S\ref{sec:limitations}. The per-class pattern is stable across seeds: \textsf{ei} ($0.98$--$1.00$) and \textsf{pi} ($0.963$) are recovered almost perfectly in every run, the variance concentrates in the seven-example \textsf{ee} class ($0.86$--$1.00$), and \textsf{pe} has recall $0$ in all five re-runs. % from exp_0073 exp_0153; seed-variance re-run seeds 42--46, experiments/exp_0073/seed_results.jsonl
We turn to the interpretation of the enhanced-track numbers and the rare-class behaviour we observed on ST3 in \S\ref{sec:discussion}.

\subsection{Final submission rationale}
\label{sec:final-submission}

We did not use the additional two-runs-per-track budget available under the Touch\'{e} submission rules. We report on the single CV-validated configuration per slot. The non-obvious choice was ST3 enhanced, where the Qwen2.5-32B single-run F1 of 0.841 sat above the RoBERTa-large dev number of 0.735 but just below the RoBERTa-large 5-fold CV mean of 0.875. % from exp_0207
Two reasons drove the encoder choice, and we keep them separate. The first is operational: the Qwen2.5-32B 5-fold cross-validation was still running at the deadline, leaving the RoBERTa-large CV as the only completed cross-validation we had in hand at submission time. The second is the absence of a statistical reason to prefer Qwen even if the comparison had been completed: a 5-fold standard deviation of $\pm$0.114 on Qwen2.5-7B is evidence the encoder-vs-LLM comparison is underpowered at this sample size, not evidence for the system whose CV mean is higher. % from exp_0180
We therefore do not claim the available CV evidence rules out the Qwen alternatives; we only claim that at deadline the encoder pipeline was the only fully-validated configuration. A post-hoc ensemble of the available encoder and LLM systems gave no gain over the single-source encoder, which is one further reason we did not retroactively complicate the submission. % from exp_0121
A submission dry-run verified that the TIRA-format outputs matched the lab's expected schema before the final upload. % from exp_0122
