This year we reflect on the structural shape of the Touch\'{e} 2026 evaluation and on what our submissions can and cannot say about it. The first three subsections below close the four contributions stated in \S\ref{sec:intro}: \S\ref{sec:disc-encoder} closes C3 (encoder vs.\ LLM at this scale), \S\ref{sec:disc-leakage} closes the first half of C4 (the enhanced-track signal), and \S\ref{sec:disc-pe} closes the second half of C4 (the \textsf{pe} rare-class limitation). \S\ref{sec:limitations} states the limitations attached to the numbers behind those subsections, and \S\ref{sec:future} lists the most useful follow-ups the present work allows.

\subsection{Encoder vs.\ LLM at this scale}
\label{sec:disc-encoder}

Across the cells we were able to validate under cross-validation, encoder fine-tuning outperformed every LLM track we evaluated. The most informative comparison is on ST3 enhanced, where the encoder's 5-fold CV mean of 0.875 sits inside the standard-deviation band of the Qwen2.5-7B CoT-LoRA comparator (0.851 $\pm$ 0.114). The single-run Qwen2.5-32B reached 0.841 on the same task. % from exp_0153 exp_0180 exp_0207
The Qwen-7B std overlaps the encoder mean, so the apparent 0.024 gap is not statistically meaningful from a single 5-fold split. The strongest claim the evidence supports is that the LLM track did not show a validated benefit at this dataset scale within our compute envelope, not that LLMs are categorically worse. We scope the claim to this dataset (roughly 473 ST3 examples), this label structure, and our compute budget; we would not extrapolate to larger labelled corpora or to richer reasoning targets.

\subsection{What the enhanced-track signal contains}
\label{sec:disc-leakage}

The 0.970 ST2-enhanced and 0.914 ST1-enhanced numbers are the strongest in the paper and warrant a careful read of what the rewritten fields contribute. The lab provides the enhanced track as a designed difficulty setting: \texttt{text\_enhanced} and \texttt{argument\_enhanced} are organiser-supplied paraphrases produced with knowledge of the gold labels, and base-only systems are scored in a separate track~\cite{kiesel:2026c}. The legitimate scientific question is therefore not whether something illicit happened (it did not) but how much of the enhanced-track lift reflects the rewrite carrying label-bearing signal versus genuine argument clarification. We address the question in four steps. % from exp_0072 exp_0035

\emph{(a) The setup.} Any classifier trained on \texttt{text\_enhanced} or \texttt{argument\_enhanced} has access to features that a base-only pipeline would have to recover from raw text. The interesting question is not whether such features exist (they are designed in) but whether the classifier is exploiting them as label strings or as cleaner argumentative structure.

\emph{(b) A sanity check, and what it does not establish.} We ran a regex-mask sanity check that replaced known fallacy-name strings and obvious cue words in the enhanced fields and re-trained the ST2-enhanced classifier on the masked inputs. F1 was retained at 0.937 after masking, against the unmasked enhanced-track \emph{baseline} (no pseudo-label) of 0.937. % from exp_0062 exp_0036
The mask deliberately covers the eight ST2 fallacy-class names and their morphological variants only, not the full semantic content of the rewritten fields. A null delta is therefore the expected outcome \emph{if} the classifier was not relying on those literal strings as a shortcut, and is the specific hypothesis the check rules out, not a general claim that the rewritten fields contain no label-bearing signal at all. We call this a sanity check rather than a diagnostic for exactly this reason: it tests a hypothesis the rewriter's design made a priori unlikely, and therefore says little about the softer semantic channel.

\emph{(c) The interpretation.} A retained F1 of 0.937 under aggressive string masking means that trivial string-matching of fallacy labels in \texttt{text\_enhanced} is not the dominant signal the classifier relies on. That rules out the most superficial story, but the rewriter could still encode the label in word choice, sentence structure, hedging, or topical framing without ever using a fallacy-name string. We note that the ST2-enhanced per-class F1 values (Appendix~\ref{app:perclass}) range from 0.889 to 1.000 on the $n=67$ dev split, with five of the eight classes at 1.000 --- a high, tight distribution still consistent with strong label-bearing signal in the rewritten fields, though the wider spread than we first reported tempers that reading slightly. % per-class F1 from exp_0072 metrics.json

\emph{(d) The reporting commitment.} We present base-track and enhanced-track numbers separately throughout this notebook and do not aggregate them into a single headline; where the paper takes a position e.g.,\ on the ablation pattern, on the encoder vs.\ LLM comparison, on the \textsf{pe} limitation, we anchor that position on base-track behaviour or 5-fold CV numbers rather than on enhanced-track point estimates. The headline enhanced-track numbers stand as ceiling results for the designed track they were produced under.

The confidence-thresholded audit gate of \S\ref{sec:pseudo} sits inside the same framing: it is one further layer of caution specifically against the pseudo-label step amplifying any label-bearing signal that survived the rewrite, and it returned no detectable issue under the test we ran. % from exp_0081
We name the limit of that gate explicitly too: it tests against the same kind of signal the masking diagnostic tests against, not against the softer semantic channel. A falsifiable extension, training a classifier on base-only fields and evaluating it on enhanced fields, would isolate the marginal contribution of the rewriter directly; we flag it in \S\ref{sec:future}.

\subsection{The \textsf{pe} rare-class limitation}
\label{sec:disc-pe}

The practical-external (\textsf{pe}) class on ST3 was the hardest scheme class in every evaluation that contained enough \textsf{pe} examples to measure it. An NLI-style basis probe flagged it early. % from exp_0082
We responded with three interventions: a \textsf{pe}-targeted synthetic batch, a per-class threshold sweep that pushed the \textsf{pe} threshold to 0.05, and an LLM basis-axis meta-learner; none lifted the class. % from exp_0103 exp_0145 exp_0146

Quantifying the gap is constrained by how few \textsf{pe} examples the dev partition holds. Our single held-out dev split contains exactly one \textsf{pe} example, so the submitted-run \textsf{pe} numbers --- F1 $=0.000$ under argmax (\texttt{exp\_0073}) and $0.25$ under the dev-only threshold sweep (\texttt{exp\_0145}), both computed on that same one-example split --- reflect a single instance rather than a distribution and cannot support a ceiling estimate. The only evaluation with meaningful \textsf{pe} support is the 5-fold cross-validation under the submitted recipe (\texttt{exp\_0153}), where \textsf{pe}-F1 averages $0.713$ across folds against a $0.875$ macro-F1, but with wide fold-to-fold variance (per-fold $0.40$--$1.00$, standard deviation $0.25$). % from exp_0073 exp_0145 exp_0153
Even there, \textsf{pe} is consistently the class that most depresses macro-F1, and the variance underlines how few \textsf{pe} instances the corpus provides; the thin \textsf{pe} representation in the dev partition is itself a limitation of the evaluation (\S\ref{sec:limitations}). The substantive finding stands: \textsf{pe} is the rare class that the targeted synthetic augmentation, the per-class threshold sweep, and the basis-axis meta-learner all failed to lift, and targeted \textsf{pe}-class data collection (\S\ref{sec:future}) is the intervention most likely to help. A five-seed re-run of the submitted recipe (Table~\ref{tab:st3cm}, \S\ref{sec:results-st3}) reinforces the point from the other direction: \textsf{ei} and \textsf{pi} are recovered almost perfectly in every run while the single \textsf{pe} dev example is misclassified in all five, so its dev F1 of $0$ reflects the split's inability to measure the class rather than a stable property of the system.

\subsection{Limitations}
\label{sec:limitations}

Several limitations should accompany the numbers in this notebook.

Every number in this initial submission is from our held-out dev partition or from 5-fold cross-validation on it; test-set leaderboard results will be incorporated in the camera-ready version. Where a single 5-fold split was available (ST3 enhanced under our submitted recipe, the Qwen2.5-7B CoT-LoRA comparator, and the Qwen3-4B-Thinking comparators) we use the CV mean as the decision-relevant estimate; the other dev numbers in Tables~\ref{tab:headline}--\ref{tab:backbone} are single-run point estimates, and the ranking of close-together rows should be read with appropriate caution. % from exp_0153 exp_0180 exp_0217 exp_0218

We ran a five-seed variance check only on the submitted ST3-enhanced cell (\S\ref{sec:results-st3}, dev macro-F1 $0.720 \pm 0.015$); we did not repeat it for the other five cells, whose reported single-run dev numbers should be read as point estimates. % from senior P1; ST3-enhanced seed-variance re-run seeds 42--46
For runs whose individual seeds are not recorded, we used the lab-default \texttt{seed=42}; CV runs used fold seeds 42--46.

The enhanced-track headline numbers are upper bounds on what the designed track can yield, in the sense developed in \S\ref{sec:disc-leakage}. The regex-mask sanity check rules out the trivial-string channel; it does not clear the softer semantic channel, and we have flagged this everywhere the enhanced numbers appear. % from exp_0062

The per-class F1 breakdown in Appendix~\ref{app:perclass} is computed under argmax decoding for both ST2 and ST3, matching the decoding used for the submitted runs and the headline numbers in Table~\ref{tab:headline}. The ST3 \textsf{pe} cell in particular rests on a single dev example and should not be read as a per-class estimate; the 5-fold cross-validation (\S\ref{sec:disc-pe}) is the only evaluation with meaningful \textsf{pe} support. % from exp_0073 exp_0153

The per-class analysis in this version of the notebook (Appendix~\ref{app:perclass} and \S\ref{sec:disc-pe}) differs from the initially submitted version. The submitted version reported a per-class breakdown whose values and supports did not trace to any saved evaluation artefact; during code--paper auditing we reconciled the analysis against the actually-submitted checkpoints (\texttt{exp\_0072}, \texttt{exp\_0073}) and now report the reproducible argmax numbers on the real dev partitions ($n=67$ and $n=69$).

Overall, these limitations do not invalidate the above numbers, but the enhanced-track results in particular should be read as upper bounds on what a fair pipeline would extract from the same inputs.

\subsection{Future work}
\label{sec:future}

The most useful follow-ups the present work allows are concrete. A falsifiable extension of the leakage diagnostic, training a classifier on base-only fields and evaluating it on enhanced fields, would isolate the marginal contribution of the rewriter and let us put a number on the residual semantic-leakage channel; we did not run this within our compute envelope and flag it as the most useful follow-up the C4 thread allows. A leakage-controlled re-evaluation on a future Touch\'{e} edition, one that ships a separate decoder for the rewritten fields, or that withholds the label-aware rewrite from training entirely, would let us decide more cleanly between the encoder and LLM tracks at this dataset scale. A larger compute budget on the Qwen2.5-32B fold split would let us close the comparison we left underpowered, addressing the open question behind C3. A per-class threshold sweep on ST3 base, paralleling the sweep we ran on ST3 enhanced, would let us test whether the \textsf{pe} limitation we observed is a property of the enhanced track or of the four-way label structure more broadly. And targeted \textsf{pe}-class data collection, rather than further synthetic augmentation, looks like the most useful intervention if the rare-class limitation is to be overcome at all.
