%% =====================================================================
%% Touché 2026 Fallacy Detection — paper.tex
%% Built on the Touché-supplied ceurart scaffold (touche24-paper.tex).
%% ceurart.cls in the project root is the workshop-supplied version
%% (verified by md5 against the 2024 template folder; the 2026 lab
%% reuses the 2024 class file).
%%
%% Year and conference fields updated for 2026; template's two-author
%% \fnmark / \fntext "equal contribution" machinery removed (single
%% author); Declaration on Generative AI added per CEUR-WS policy
%% (mandatory since 2024-12-20); body sections enter via \input.
%% =====================================================================

\documentclass{ceurart}
\sloppy

%% Project additions. ceurart.cls already loads graphicx, booktabs,
%% multirow, array, microtype, natbib, geometry, hyperref, xcolor —
%% so we only add what the class does not provide.
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,shapes.geometric,fit,backgrounds,calc}

\usepackage[most]{tcolorbox}
\tcbuselibrary{skins,breakable}

% Prompt-box style matching BIT.UA at BioASQ 13B (CEUR-WS Vol-4038, paper_22).
% Rounded outer frame, solid black header strip with the prompt label in white,
% body in the document's normal body font.
\newtcolorbox{promptbox}[1]{%
  enhanced,
  breakable,
  colback=white,
  colframe=black,
  boxrule=0.4pt,
  arc=2pt,
  left=6pt, right=6pt, top=6pt, bottom=6pt,
  fonttitle=\bfseries\sffamily\small,
  coltitle=white,
  colbacktitle=black,
  attach boxed title to top left={xshift=0pt, yshift=0pt},
  boxed title style={
    colback=black,
    colframe=black,
    boxrule=0pt,
    arc=2pt,
    left=6pt, right=6pt, top=2pt, bottom=2pt,
  },
  title={#1},
}

\copyrightyear{2026}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

\conference{CLEF 2026: Conference and Labs of the Evaluation Forum,
  September 21--24, 2026, Jena, Germany}

\begin{document}

%% ---------------------------------------------------------------------
%% Title and sub-title (Touché lab convention)
%% ---------------------------------------------------------------------
\title{UZHCL\_for\_the\_win at Touch\'{e}: Encoder Fine-Tuning, Synthetic Augmentation, and an Underpowered Encoder--LLM Comparison}
\title[mode=sub]{Touch\'{e} at CLEF 2026}

%% ---------------------------------------------------------------------
%% Author block. ORCID remains a pre-camera-ready TODO.
%% ---------------------------------------------------------------------
\author[1]{Stylianos Psychias}[%
  email=stylianos.psychias@uzh.ch,
]
\address[1]{University of Zurich, Zurich, Switzerland}

%% ---------------------------------------------------------------------
%% Abstract and keywords (both mandatory in ceurart)
%% ---------------------------------------------------------------------
\begin{abstract}
Online discussions on platforms like Reddit are a productive testbed for fallacy detection: short texts, broad topical range, and the full inventory of informal fallacies catalogued by classical argumentation theory long before social media. The Touch\'{e} 2026 lab at CLEF formalises this as a shared task on a Reddit-derived corpus and provides a structured benchmark for systems that combine fallacy detection with argument-scheme classification. This paper describes our participation in the lab, covering all three subtasks (ST1 binary fallacy detection, ST2 eight-way fallacy classification, ST3 four-way argument-scheme classification) and both evaluation tracks. Our submitted systems are fine-tuned RoBERTa-large encoders with task-specific heads, augmented with a small batch of LLM-generated synthetic contrastive pairs; for ST2 and ST3 on the enhanced track we additionally extended training with pseudo-labelled examples, extra training items that the encoder labels itself from the published unlabelled pool, kept only where it is most confident and only after a verification check has passed. As an alternative to the submitted pipeline we ran a wider backbone comparison spanning additional encoders (DeBERTa-v3, ModernBERT) and an LLM track (four Qwen variants: 3B zero-shot and kNN few-shot, 7B and 32B CoT-LoRA, and Qwen3-4B-Thinking); under our compute envelope and at this corpus scale, none of these configurations showed a validated benefit over the submitted RoBERTa-large encoder, with a 5-fold standard deviation wide enough that we report the comparison as underpowered rather than settled. The enhanced track is the lab's designed difficulty setting: the organisers deliberately rewrote the input fields to surface fallacy and scheme structure, and base- and enhanced-track systems are evaluated separately. We characterise how much of the enhanced-track lift comes from the rewrite carrying label information versus genuine argument clarification, and we anchor cross-comparisons on base-track or 5-fold CV behaviour where the question matters. On our held-out development partitions the submitted systems perform strongly across all six (subtask, track) cells. On the official Touch\'{e} 2026 test set they ranked first on both base-track classification cells (ST2 and ST3) and second on both binary-detection (ST1) tracks, with the two enhanced-track classification cells topped by cascaded and multitask systems. We close on the practical-external rare-class limitation on ST3, the limitations of the present work, and the most useful follow-ups. All code is publicly available at \url{https://github.com/psychias/fallacy_detection_clef_2026}.
\end{abstract}

\begin{keywords}
  Fallacy detection \sep
  Argument scheme classification \sep
  Touch\'{e} 2026 \sep
  RoBERTa \sep
  Synthetic data augmentation \sep
  Pseudo-labelling
\end{keywords}

\maketitle

%% =====================================================================
\section{Introduction}
\label{sec:intro}
\input{sections/01_introduction.tex}

%% =====================================================================
\section{Previous Work}
\label{sec:background}
\input{sections/02_previous_work.tex}

%% =====================================================================
\section{Methodology}
\label{sec:system}
\input{sections/03_methodology.tex}

%% =====================================================================
\section{Results}
\label{sec:results}
\input{sections/04_results.tex}

%% =====================================================================
\section{Discussion and Future Work}
\label{sec:discussion}
\input{sections/05_discussion.tex}

%% =====================================================================
\section{Conclusion}
\label{sec:conclusion}
\input{sections/06_conclusion.tex}

%% =====================================================================
%% Acknowledgments (ceurart environment; placed before back matter
%% per the formatting-instructions PDF).
%% =====================================================================
\begin{acknowledgments}
The author thanks the Touch\'{e} 2026 lab organizers for providing
the dataset, evaluation infrastructure, and submission platform.
\end{acknowledgments}

%% =====================================================================
%% AI Usage Declaration. CEUR-WS policy (mandatory since 2024-12-20)
%% requires a Declaration on Generative AI; the section heading and
%% wording below follow the author's preferred template.
%% =====================================================================
\section*{AI Usage Declaration}
This text was proofread and improved with the assistance of
Claude (Anthropic). The following prompt was used:

\begin{quote}
``Imagine you're an AI master student. Evaluate my text based on the
task description and check if it correct or not, if not tell me which
parts I should improve.''
\end{quote}

\noindent Claude was used to evaluate the text against the
Touch\'{e} 2026 Fallacy Detection task description, identify missing
elements (results coverage, leakage handling, methodology and ablation
details) and suggest phrasing improvements. The author conceived and
executed all experiments, made all submission decisions, and takes full
responsibility for the publication's content.

%% =====================================================================
%% Bibliography
%% =====================================================================
\bibliography{references}

%% =====================================================================
\appendix

\section{Prompts}
\label{app:prompts}

Synthetic contrastive pairs and pseudo-labelled examples contributed to
the submitted systems (\S\ref{sec:synth}, \S\ref{sec:pseudo}). The system
prompts that drove each generation batch are reproduced verbatim below;
the matching user prompts are built per call from a topic seed, a
subreddit, a small block of real exemplars from the train split, a
sampled target length and number of supports, and (for ST1/ST2) a
fallacy card or (for ST3) a scheme pair. Generated batches are released
alongside this notebook in the TIRA submission package.

\medskip

\begin{promptbox}{Prompt 1: ST1/ST2 contrastive-pair generation.
System message.}
You generate training data for a fallacy detection model. The data
must read as authentic Reddit replies: informal register, hedges
(``idk'', ``tbh'', ``iirc''), occasional typos, no debate-club
phrasing, no signposting. Never name the fallacy inside the
generated text.

The `load-bearing signals' you'll be shown describe the LOGICAL
PATTERN of the fallacy, not phrases to use verbatim. Express the
same reasoning move with fresh wording. Do NOT use any of these
stock formulations (fresh wording only): `millions of people
can't be wrong', `people can't be wrong', `everyone knows',
`no middle ground', `no in between', `before you know it',
`next thing you know', `where does it end', `it's a slippery
slope', `we've always done it', `natural is better', `chemicals
are bad', `yeah i agree', `i agree it's'. If your draft contains
any of these phrases, rewrite the draft.

You will produce a CONTRASTIVE PAIR: one reply that commits the
target fallacy, and one reply using structurally similar reasoning
that does NOT commit it. Both replies must address the same topic
with claims of similar polarity, so the only meaningful difference
is the soundness of the inference.

CRITICAL: Do NOT cite specific percentages, year-tagged studies
(e.g.\ `2023 study'), polls, named institutions (Gallup, Pew, CDC,
etc.), or made-up statistics in EITHER reply. Both replies must
reason from lived experience, anecdote, observation, or general
claims. The difference between them is the soundness of the
inference, not the presence of evidence.
\end{promptbox}

The user prompt supplies a fallacy card (definition, load-bearing
signals, legitimate counterpart), the topic and subreddit, a target
length and per-reply support count, and a small block of real
exemplars. The model returns a JSON object carrying \texttt{thread\_title},
\texttt{parent}, and two replies (\texttt{fallacious} and
\texttt{legitimate}), each with \texttt{text\_raw}, \texttt{text\_base},
\texttt{claim}, and \texttt{supports}.

\medskip

Prompt 2 has the same shape as Prompt 1, but produces two
non-fallacious replies using different argumentation schemes.

\begin{promptbox}{Prompt 2: ST3 contrastive-pair generation
(\texttt{synth\_v002} ST3). System message.}
You generate training data for an argumentation scheme classifier.
The data must read as authentic Reddit replies: informal register,
hedges, occasional typos, natural conversation. No academic phrasing.

[blocklist as in Prompt 1]

You will produce a CONTRASTIVE PAIR: two non-fallacious replies to
the same parent comment, on the same topic, with similar conclusions
-- but using DIFFERENT argumentation schemes. The structural
difference should be clear but natural.
\end{promptbox}

The user prompt specifies Scheme A (target) and Scheme B (contrast),
each with goal axis (practical / epistemic), basis axis (internal /
external), definition, and load-bearing signals, together with the
topic, subreddit, target length, and exemplar block. JSON output is
\texttt{scheme\_a} / \texttt{scheme\_b}, each with \texttt{scheme},
\texttt{argument\_goal}, \texttt{argument\_basis}, \texttt{text\_raw},
\texttt{text\_base}, \texttt{claim}, and \texttt{supports}.

\medskip

A separate, simpler prompt generated the \textsf{pe}-targeted batch
(50 examples per label, \texttt{openai/gpt-4o-mini}, temperature 0.9).

\begin{promptbox}{Prompt 3: \textsf{pe}-targeted generation
(\texttt{exp\_0103}). System message.}
You are an expert in argumentation theory and propaganda techniques.
Generate realistic argumentative text snippets that contain propaganda
or emotional manipulation techniques (loaded language, fear appeals,
bandwagon, false dilemma, etc.) rather than logical reasoning.

The text should be 2-4 sentences, resemble real-world political
discourse or persuasive media, and clearly exemplify propaganda /
emotional fallacies.
\end{promptbox}

\medskip

\noindent Two user prompts, one per generated label:

\begin{promptbox}{Prompt 3: \textsf{pe}-targeted generation
(\texttt{exp\_0103}). User prompts.}
\textbf{[pe]}\quad Generate a short argumentative text (2-4 sentences)
that uses propaganda or emotional manipulation. Include at least one
of: loaded language, appeal to fear, bandwagon appeal, false dilemma,
or emotional blackmail. Make it sound like real political/media
discourse.

\textbf{[pa]}\quad Generate a short argumentative text (2-4 sentences)
that primarily appeals to emotion (pathos) rather than logic. Use
emotional language, fear, pity, or desire to persuade. Make it
realistic.
\end{promptbox}

\paragraph{Pseudo-label confidence selection (\texttt{exp\_0072},
\texttt{exp\_0073}).}
The pseudo-labelling step filtered the encoder classifier's own
predictions at a nominal $\tau=0.9$, relaxed for under-populated classes
so that rare schemes were retained (see \S\ref{sec:pseudo}); it is not LLM-API
driven and uses no prompt. We list it here for completeness rather
than because there is a prompt to record.

%% =====================================================================
\section{Hyperparameter Grid}
\label{app:hyper}

Table~\ref{tab:hyper} summarises the configurations used for the six submitted runs.
All runs share the RoBERTa-large backbone~\cite{liu2019roberta} and use the
\texttt{transformers} library~\cite{wolf2020transformers}. Optimiser is AdamW with
linear warmup over the first 10\% of steps. Loss is class-weighted cross-entropy for ST2 and ST3;
ST1 uses unweighted cross-entropy. Where the experiment log does not separately record a seed,
we used the lab default \texttt{seed=42}; 5-fold CV runs used fold seeds 42--46.

\begin{table}[h]
\centering
\small
\caption{Submitted-run hyperparameter grid. \texttt{sw} is the loss weight applied to
synthetic (and pseudo-labelled) examples relative to real examples. \texttt{max\_len}
is the tokeniser truncation length.}
\label{tab:hyper}
\begin{tabular}{llcccccc}
\toprule
Subtask & Track & exp\_id & max\_len & batch & lr & epochs & extras \\
\midrule
ST1 & base     & exp\_0161 & 512 & 8 & 1e-5 & 12 & synth\_v002 sw=0.5, raw\_concat \\ % from exp_0161
ST1 & enhanced & exp\_0035 & 256 & 8 & 1e-5 & 12 & synth\_v002 sw=0.5 \\ % from exp_0035
ST2 & base     & exp\_0032 & 256 & 8 & 1e-5 & 15 & synth\_v002 sw=0.5 \\ % from exp_0032
ST2 & enhanced & exp\_0072 & 384 & 8 & 1e-5 & 12 & synth + pseudo sw=0.3 \\ % from exp_0072
ST3 & base     & exp\_0069 & 384 & 8 & 1e-5 & 15 & synth\_v002 sw=0.5 \\ % from exp_0069
ST3 & enhanced & exp\_0073 & 384 & 8 & 1e-5 & 15 & synth + pseudo sw=1.0 \\ % from exp_0073
\bottomrule
\end{tabular}
\end{table}

Synthetic generation used a frontier LLM via API (see \S\ref{sec:system});
the prompt template and the generated pairs are released alongside this
notebook in the TIRA submission package. Per-class decision thresholds for
ST3 were swept on the dev partition; the best configuration was
$\{\text{ee}{=}0.1, \text{ei}{=}0.1, \text{pe}{=}0.05, \text{pi}{=}0.4\}$
(\texttt{exp\_0145}, $+0.026$ F1 over default argmax on the dev partition; this sweep was a dev-partition diagnostic and was not applied to the submitted predictions, which use argmax). % from exp_0145

%% =====================================================================
\section{Per-Class F1 on the Dev Partition}
\label{app:perclass}

Table~\ref{tab:perclass} reports per-class precision, recall, F1, and
support for the submitted enhanced-track systems on the held-out
development partition. Both ST2 (\texttt{exp\_0072}) and ST3
(\texttt{exp\_0073}) values are computed from default argmax predictions
--- the decoding actually used for the submitted runs --- and are read
directly from each checkpoint's saved metrics ($n=67$ for the ST2 dev
split, $n=69$ for ST3). Both macro-F1 values reconcile with
Table~\ref{tab:headline} (\S\ref{sec:results}) within $\pm 0.001$
rounding. This breakdown was reconciled against the submitted checkpoints
during code--paper auditing, replacing an earlier table whose per-class
values and supports did not correspond to any saved evaluation artefact.

\begin{table}[h]
\centering
\small
\caption{Per-class precision, recall, F1, and support on the dev
partition for ST2-enhanced (\texttt{exp\_0072}, $n=67$) and ST3-enhanced
(\texttt{exp\_0073}, $n=69$), both under argmax decoding. Values are read
from the submitted checkpoints' saved metrics. The ST3 \textsf{pe} cell
rests on a single dev example and is not an informative per-class
estimate (see \S\ref{sec:disc-pe}).}
\label{tab:perclass}
\begin{tabular}{lcccc}
\toprule
Label & Precision & Recall & F1 & Support \\
\midrule
\multicolumn{5}{l}{\textit{ST2 (8-way; exp\_0072; argmax; $n=67$)}} \\ % from exp_0072 metrics.json
authority             & 1.000 & 1.000 & 1.000 & 8 \\
black-white           & 1.000 & 1.000 & 1.000 & 8 \\
hasty-generalization  & 1.000 & 1.000 & 1.000 & 8 \\
natural               & 1.000 & 0.889 & 0.941 & 9 \\
population            & 0.875 & 1.000 & 0.933 & 7 \\
slippery-slope        & 1.000 & 1.000 & 1.000 & 9 \\
tradition             & 0.889 & 0.889 & 0.889 & 9 \\
worse-problems        & 1.000 & 1.000 & 1.000 & 9 \\
\midrule
\multicolumn{5}{l}{\textit{ST3 (4-way; exp\_0073; argmax; $n=69$)}} \\ % from exp_0073 metrics.json
ee (epistemic-external) & 1.000 & 1.000 & 1.000 & 7 \\
ei (epistemic-internal) & 1.000 & 0.958 & 0.979 & 48 \\
pi (practical-internal) & 0.929 & 1.000 & 0.963 & 13 \\
pe (practical-external) & 0.000 & 0.000 & 0.000 & 1 \\
\bottomrule
\end{tabular}
\end{table}

%% =====================================================================
\section{ST3-Enhanced Confusion Matrix}
\label{app:st3cm}

Table~\ref{tab:st3cm} gives a representative dev confusion matrix for the
ST3-enhanced system. The submitted run's logits were not checkpointed, so its
exact matrix is unrecoverable; the training script now saves per-example dev
logits (\texttt{dev\_logits.npz}), and we re-ran the \texttt{exp\_0073} recipe
under five seeds on the same fixed dev split (\S\ref{sec:results-st3}). The
matrix shown is the run nearest the five-seed mean (macro-F1 $0.722$). The
qualitative structure is stable across seeds: \textsf{ei} and \textsf{pi} are
recovered almost perfectly, the residual errors sit in the small \textsf{ee}
class, and the single \textsf{pe} example is misclassified in every run
(\S\ref{sec:disc-pe}).

\begin{table}[h]
\centering
\small
\caption{Representative dev confusion matrix for ST3-enhanced (\texttt{exp\_0073}
recipe, seed nearest the five-seed mean; macro-F1 $0.722$, $n=69$). Rows are the
gold label, columns the argmax prediction. Reconstructed from the released
\texttt{dev\_logits.npz}.}
\label{tab:st3cm}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{Predicted} \\
\cmidrule(l){2-5}
True & \textsf{ee} & \textsf{ei} & \textsf{pi} & \textsf{pe} \\
\midrule
\textsf{ee} (epistemic-external) & 6 & 0 & 0 & 1 \\
\textsf{ei} (epistemic-internal) & 0 & 48 & 0 & 0 \\
\textsf{pi} (practical-internal) & 0 & 0 & 13 & 0 \\
\textsf{pe} (practical-external) & 0 & 0 & 1 & 0 \\
\bottomrule
\end{tabular}
\end{table}

%% =====================================================================
\section{Citation Graph}
\label{app:citgraph}

Figure~\ref{fig:citgraph} traces the prior work that fed each component of
our pipeline. The horizontal axis is left-to-right: citations on the left,
the pipeline stages they motivated on the right. Solid arrows mark routes
that ended up in the submitted system; dashed arrows mark routes we tried
and abandoned (the DeBERTa-v3-large NaN failures, ModernBERT-large
underperformance, and the LLM alternative that did not validate under CV).

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  node distance = 5mm and 18mm,
  font          = \footnotesize,
  every node/.style = {align=center},
  citebox/.style = {draw, rounded corners=2pt, inner sep=3pt,
                    minimum width=40mm, minimum height=8mm,
                    line width=0.4pt},
  pipebox/.style = {draw, rounded corners=2pt, inner sep=3pt,
                    minimum width=46mm, minimum height=10mm,
                    line width=0.4pt},
  blue/.style   = {citebox, fill=blue!8,   draw=blue!55!black},
  teal/.style   = {citebox, fill=teal!10,  draw=teal!55!black},
  gray/.style   = {citebox, fill=black!5,  draw=black!55},
  purp/.style   = {citebox, fill=violet!8, draw=violet!55!black},
  amber/.style  = {citebox, fill=orange!10,draw=orange!65!black},
  ptl/.style    = {pipebox, fill=teal!10,  draw=teal!55!black},
  pgr/.style    = {pipebox, fill=black!5,  draw=black!55},
  pam/.style    = {pipebox, fill=orange!10,draw=orange!65!black},
  ppu/.style    = {pipebox, fill=violet!8, draw=violet!55!black},
  solid/.style  = {-{Latex[length=2mm]}, line width=0.5pt},
  dropped/.style= {-{Latex[length=2mm]}, line width=0.5pt, dashed,
                   draw=black!55},
]

% Left column: citations
\node[blue]  (c1)                            {Sahai et al.\ 2021\\\textit{Source dataset}};
\node[blue,  below=of c1] (c2)               {Macagno 2022\\\textit{Goal/basis axes}};
\node[blue,  below=of c2] (c3)               {Kiesel et al.\ 2026\\\textit{Lab overview}};
\node[teal,  below=8mm of c3] (c4)           {Liu et al.\ 2019 (RoBERTa)\\\textit{Chosen backbone}};
\node[gray,  below=of c4] (c5)               {He et al.\ 2021 (DeBERTa-v3)\\\textit{Abandoned, NaN}};
\node[gray,  below=of c5] (c6)               {Warner et al.\ 2024\\\textit{ModernBERT --- tried, lost}};
\node[purp,  below=8mm of c6] (c7)           {Qwen 2024 / 2025\\\textit{Qwen2.5, Qwen3}};
\node[purp,  below=of c7] (c8)               {Hu 2022 / Wei 2022\\\textit{LoRA + CoT}};
\node[amber, below=8mm of c8] (c9)           {Lee 2013 / Mukherjee 2020\\\textit{Pseudo-labelling}};
\node[gray,  below=of c9] (c10)              {Fr\"{o}be et al.\ 2023\\\textit{TIRA platform}};

% Right column: pipeline
\node[ptl, right=of c2, yshift=4mm]   (p1) {Data preparation\\\textit{base and enhanced fields}};
\node[ptl, right=of c4, yshift=2mm]   (p2) {RoBERTa-large fine-tuning\\\textit{max\_len 384, lr 1e-5}};
\node[pam, right=of c9, yshift=-3mm]  (p3) {Synth + pseudo augmentation\\\textit{sw 0.3--1.0}};
\node[ppu, below=of p3]               (p4) {LLM exploration\\\textit{Qwen + CoT-LoRA, not shipped}};
\node[pgr, below=of p4]               (p5) {TIRA submission\\\textit{6 slots, RoBERTa-large}};

% Edges: chosen routes
\draw[solid] (c1.east) -- (p1.west);
\draw[solid] (c2.east) -- (p1.west);
\draw[solid] (c3.east) -- (p1.west);
\draw[solid] (c4.east) -- (p2.west);
\draw[solid] (c9.east) -- (p3.west);
\draw[solid] (c10.east) -- (p5.west);

% Edges: dropped routes
\draw[dropped] (c5.east) -- (p2.west);
\draw[dropped] (c6.east) -- (p2.west);
\draw[dropped] (c7.east) -- (p4.west);
\draw[dropped] (c8.east) -- (p4.west);

% Internal flow on the right
\draw[solid] (p1.south) -- (p2.north);
\draw[solid] (p2.south) -- (p3.north);
\draw[solid] (p3.south) -- (p4.north);
\draw[solid] (p4.south) -- (p5.north);
\draw[solid] (p2.east) to[bend left=10] (p5.east);

\end{tikzpicture}
\caption{Which prior work fed which component of our pipeline. Solid
arrows are routes that shipped; dashed arrows are routes we tried
and dropped (DeBERTa-v3-large under NaN, ModernBERT-large
underperforming RoBERTa-large, and the LLM alternative that did not
out-perform RoBERTa-large under cross-validation within our compute
envelope).}
\label{fig:citgraph}
\end{figure}

\end{document}
